Unfolding the City: \wq{Exploring Urban Spatial Attractiveness with Individual Social Characteristics}

### 2019-05-03 manuscript/template.tex
new one 0503, with all figures in draft format

\title{Unfolding the City: \wq{Exploring Urban Spatial Attractiveness with Individual Characteristics}}
%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}

@@

\section{Overview}
\wqc{Adding a background. Expert discussion. Summarize the tasks below.-0419}
\lmc{Add a paragraph to introduce the motivation of this work, where we derive the tasks via the interview with domain exports.-0420}

@@

\begin{itemize}

  \item \textit{Magnitude of spatial attractiveness} How many persons could be attracted and how much the difficulty they overcome. \wqc{there is equation in related paper to support this.} \lmc{can you expand the spatial attractivenss, such as citing existing paper, explaining the concept, maybe with the equation is better.}

  \item \textit{Diversity of spatial attractiveness} Two types of diversity: diversity of the attracted persons, and diversity of attractiveness indicators. \wqc{cannot find this concept in papers, and, i am not sure about ``indicator"} \lmc{I defined this?}

\end{itemize}
With these questions, we summarize them into the tasks below, which need to be answered by our system.

@@

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\linewidth]{pictures/interfaceDraft.eps}
 \caption{\wq{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) View1: a XXXX visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) View2: data-driven profiles support users with organic individual perception; (d) View3: map view for movement of the chosen group; (e) View4: for ranking or comparison; (g) View5: top N kinds of citizens with social characteristics.}}
 \label{fig:interfaceDraft}
\end{figure}

@@

Glyph-based visualization~\cite{borgo2013glyph} is the form of visual design to compose multivariable into a collection of unified visual symbols, known as a glyph. A glyph is intended for quick understanding and aligned comparison. \lm{Dual glyphs are designed, to illustrate the information of individual from two different perspectives, i.e., detailed inspection of individuals and efficient comparsion over multiple individuals.}

@@

@@

\wq{\subsection{XXXX Projection of Individuals}}
\wqc{A octagon radar graph to position all citizens. A clustering algorithm for commend similar persons into a new group.(maybe: interactions to set the weight of each characteristic)} \lmc{Yes, I think an interactive weight adjustment is good.}

@@

\iffalse
\subsection{2.5D Spatial Visualization}
\label{subsec:25D}

\begin{figure}[htb!]
\centering
\subfigure[]{
\resizebox*{9cm}{!}{\includegraphics{pictures/space1.eps}}}\hspace{5pt}
\subfigure[]{
\resizebox*{9cm}{!}{\includegraphics{pictures/space2.eps}}}\hspace{5pt}
\caption{2.5D Spatial Visualization: (a) 2.5D spatial visualization with z-axis to encode addition information; (b) detail slicing in 2.5D space.}
\label{fig:2.5D}
\end{figure}

Embedding multiple variables in the spatial map is a challenging problem. Distorting 2D spatial for better space usage, such as the partial route embedding~\citep{sun2016embedding} is an effective method when there are a few local foci. When it comes to the global visualization, there is always a trade-off between occlusion-free and the compact spatial perception. Following the idea of stacking 2.5D space design~\citep{Tominski2012_stacking}, the space in this work is embedded in 2.5D space, to relax the z-axis for additional abstract information encoding.

Figure~\ref{fig:2.5D}(a) shows the 2.5D visualization. The spatial map consists of Traffic Analysis Zone (TAZ), which is the unit of geography holding a certain number of people. For the 2.5D, each TAZ is grown as a prism whose height and color are developed to encode abstract information, e.g., the occurrence of visiting. With difference encoding choices, it is capable to visualize the correlation between spatial and different attributes (\textit{C4}). For example, in Figure~\ref{fig:2.5D}(a), prisms' height and color both encode the ratio of none-routine trips (such as go entertainment, go hospital, etc.) in the whole. For better 3D visual perception, lighting is turned on. Also, a lid is laid on the top of each prism to clearly bound its extent at the z-axis.

Several interactions are integrated into the spatial view to alleviating the occlusion problem (\textit{C5}). The manipulation of 2.5D view supports users with rotate, zoom, pan operations, which are so continuously flexible that users probably find a suitable observing point. In the cases where occlusion is inevitable, an interaction named as \textit{Detail Slicing} is developed, as Figure~\ref{fig:2.5D}(b) shows. Detail Slicing is the operation to put a cross-section in the 2.5D space to expose the TAZ inside. To contextualize the cross-section, TAZs are visually adapted according to the intersection by ray casting. The TAZ in the foreground will be hidden, the intersected TAZs will be fully visualized and the ones in the background will be in semi-transparency.

To compare the mobility patterns across different groups of people, a Small Multiple dock is used to reserve the ever explored interesting result (Figure~\ref{fig:teaser}(f)). To simply the comparison over spatial distribution, the snapshot is also rendered in the 2.5D space, which maintains the same interactions as the main 2.5D space does.
\fi

\wq{\subsection{A glyph design to show travel indicator (in view3, in case1)}
We design a kind of glyph to express a high-dimensional travel indicators. It will be embeded in the map view\wqc{for case1}. \lmc{This is great! more indicators, the better. }
The elements may be included in the glyph:
\begin{itemize}
  \item (home-work distance)
  \item travel distance
  \item travel radius
  \item travel frequency
\end{itemize}}

\wq{\subsection{A glyph design to show attractiveness (in view3, in case2)}
We design a kind of glyph to express spatial attractiveness.
The elements may be included in the glyph: \lmc{We can explain each of the indicator a bit. But do it later after the implementation.}
\begin{itemize}
  \item quantity
  \item distance
\end{itemize}}

\wq{\subsection{A glyph design to show attractiveness diversity(in view3, in case3)}
We design a kind of glyph to express spatial attractiveness.
The elements may be included in the glyph: \lmc{we need to find terms similar to above}
\begin{itemize}
  \item \lm{Purpose Number} how many kinds of purpose?
  \item  the percentage of each purpose?
\end{itemize}

(if comparison between groups, the glyph up, show the diversity of multiple groups at the same time.)}

@@

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case1draft}
 \caption{Home Distributions of the Four Groups}
 \label{case1draft}
\end{figure}

@@

\subsection{Case 2: Diversity of spatial attractiveness of indicators}
\wqc{aim: with mixed purposes, show attractiveness quantity and entropy. View3 shows spatial attractiveness, including: quantity, distance, （direction）; View4 shows ranking of origins, (or others); (add a interaction in view5 for citizens in selected grid.)}

@@

\wq{As Figure~\ref{case2draft} shows, in view3, glyph represents $\textbf{the quantity}$ and $\textbf{value of mixture of purposes}$. \wqc{(if we decide to give a computing equation to define it.)}\lmc{I think we can define a equation to compute it.} in view 4, ranking of each grid based on the quantity of each purpose.}
\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case2draft}
 \caption{Trip purposes distribution of four groups with different jobs}
 \label{case2draft}
\end{figure}

@@

\subsection{Case 3: Magnitude of Spatial Attractiveness}
\wqc{aim: select one purpose to show how many and where and how long. Use View3 and view4.} 
\lmc{So as far as I understand, in this case, we focus on exploring the attributes or properties of spatial attratctiveness, right? such as the number, distance, origins, etc.}

\wq{As Figure~\ref{case3draft} shows, in view3, glyph represents $\textbf{the quantity}$ and $\textbf{how many grids are linked(i.e. area)}$ and $\textbf{distribution of distances}$. in view4, show $\textbf{where are the linked grids}$ and $\textbf{the quantity of each linked grid}$ and $\textbf{distance}$. \wqc{not sure the form in view4, map or chart? if map, 1D or 2.5D?}}
\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case3draft}
 \caption{Home-work distances of different groups: (a) with different salary levels; (b) with or without house.}
 \label{case3draft}
\end{figure}

>>>>

\title{Unfolding the City: \wq{Exploring Urban Spatial Attractiveness with Individual Social Characteristics}}
%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}

@@

\section{Overview}

@@

\begin{itemize}
  \item \textit{Spatial attractiveness} How many persons could be attracted and how much the difficulty they overcome. \wqc{there is equation in related paper to support this.} \lmc{can you expand the spatial attractivenss, such as citing existing paper, explaining the concept, maybe with the equation is better.}

  \item \textit{Diversity of spatial attractiveness} Two types of diversity: diversity of the attracted persons, and diversity of attractiveness indicators. \wqc{cannot find this concept in papers, and, i am not sure about ``indicator"} \lmc{I defined this?}
\end{itemize}
With these questions, we summarize them into the tasks below, which need to be answered by our system.

@@

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\linewidth]{pictures/interface53}
 \caption{\wq{System Interface: (a) an interactive infographics provides the basic statistic facets of individuals; (b) View1: a XXXX visualization gives an overview of individuals, where the similarity in high dimensional space is preserved in 2D space; (c) View2: data-driven profiles support users with organic individual perception; (d) View3: map view for movement of the chosen group; (e) View4: for ranking or comparison; (g) View5: top N kinds of citizens with social characteristics.}}
 \label{fig:interfaceDraft}
\end{figure}

@@

Glyph-based visualization~\cite{borgo2013glyph} is the form of visual design to compose multivariable into a collection of unified visual symbols, known as a glyph. A glyph is intended for quick understanding and aligned comparison. \lm{Dual glyphs are designed, to illustrate the information of individual from two different perspectives, i.e., detailed inspection of individuals and efficient comparison over multiple individuals.}

@@

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\linewidth]{pictures/star53}
 \caption{\wq{star-like glyph for a group of citizens.}}
 \label{fig:interfaceDraft}
\end{figure}

@@

\subsection{T-SNE Projection}

@@

\subsection{HAVE NO TILE FOR THIS}
We design a kind of glyph to express a high-dimensional travel indicators. It will be embeded in the map view. \wqc{lack of a FIGURE}

The elements can be represented in the glyph:
\begin{itemize}
  \item value
  \item distribution
  \item proportion
\end{itemize}

@@

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/c1-s3-53}
 \caption{Home Distributions of the Four Groups}
 \label{case1draft}
\end{figure}

@@

\subsection{Case 2: Spatial Attractiveness}
\wqc{aim: select one purpose to show how many and where and how long.}
\lmc{So as far as I understand, in this case, we focus on exploring the attributes or properties of spatial attratctiveness, right? such as the number, distance, origins, etc.}

\wq{As Figure~\ref{case3draft} shows, in view3, glyph represents $\textbf{the quantity}$ and $\textbf{how many grids are linked(i.e. area)}$ and $\textbf{distribution of distances}$. }
\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/c2-s2-53}
 \caption{For purpose of shopping: (a) the rich; (b) the poor.}
 \label{case3draft}
\end{figure}

\wq{After clicking a target grid, show $\textbf{where are the linked grids}$ and $\textbf{the quantity of each linked grid}$ and $\textbf{distance}$. Compare two grid which have similar quantity, the distributions differ.}
\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/c2-click-s2-53}
 \caption{For purpose of shopping: (a) spatial attractiveness of the poor; (b) Grid1; (c) Grid2.}
 \label{case3draft}
\end{figure}

\subsection{Case 3: Diversity of spatial attractiveness of indicators}
\wqc{aim: with mixed purposes, show attractiveness quantity and entropy. View3 shows spatial attractiveness, including: quantity, distance, （direction）; View4 shows ranking of origins, (or others); (add a interaction in view5 for citizens in selected grid.)}

@@

\wq{As Figure~\ref{case2draft} shows, in view3, glyph represents $\textbf{the quantity}$ and $\textbf{value of mixture of purposes}$. \wqc{(if we decide to give a computing equation to define it.)}\lmc{I think we can define a equation to compute it.} in view 4, ranking of each grid based on the quantity of each purpose.}
\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/c3-53}
 \caption{Trip purposes distribution of four groups with different jobs}
 \label{case2draft}
\end{figure}

@@
